On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-04-16 document/ieee_trans/det_ieeetrans.tex
a few typos corrected

Greg Chance (e-mail: greg.chance@bristol.ac.uk), 
Abanoub Ghobrial (e-mail: abanoub.ghobrial@bristol.ac.uk), 
Kevin McAreavey (e-mail: kevin.mcareavey@bristol.ac.uk), 
and 
Kerstin Eder (e-mail: kerstin.eder@bristol.ac.uk) 
are with the Trustworthy Systems Lab, Department of Computer Science, University of Bristol, Merchant Ventures Building, Woodland Road,  Bristol, BS8 1UQ, United Kingdom.

S\'everin Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
Tony Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England,Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/tony}}]{Tony Pipe} 
received his BSc (Hons.) degree in Electronic Engineering from Warwick in 1979 and, after an eight-year period in industry that included running a small company, received his PhD in Robotics from the University of the West of England (UWE) in 1997. Since 2010 he has been a Professor of Robotics and Autonomous Systems at UWE. He was a founding member of the Bristol Robotics Laboratory (BRL), and acted as one of its two Deputy Directors from its inception in 2006 until 2020. His research interests focus on safe and correct operation whilst in close-proximity to human beings. He has co-authored over 200 international refereed publications, supervised 35 PhDs, and created a BRL income of \pounds£10M since 2013. He has acted as BRL-UWE PI on the EPSRC grant ‘Trustworthy Robotic Assistants’, the Programme/Hub grants ‘Robotics for Nuclear Environments’ and ‘National Centre for Nuclear Robotics’, and the Centre for Doctoral Training in Robotics and Autonomous Systems. Prof. Pipe has been involved with Connected Autonomous Vehicle research and development since 2015 via the Innovate UK/CCAV funded projects VENTURER, FLOURISH, MultiCAV, CAPRI, ROBOPILOT and CAV-Forth.
\end{IEEEbiography}

>>>>

Greg Chance (e-mail: greg.chance@bristol.ac.uk), 
Abanoub Ghobrial (e-mail: abanoub.ghobrial@bristol.ac.uk), 
Kevin McAreavey (e-mail: kevin.mcareavey@bristol.ac.uk), 
and 
Kerstin Eder (e-mail: kerstin.eder@bristol.ac.uk) 
are with the Trustworthy Systems Lab, Department of Computer Science, University of Bristol, Merchant Ventures Building, Woodland Road, Bristol, BS8 1UB, United Kingdom.

S\'everin Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
Tony Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England, Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{../other/mugs/tony}}]{Tony Pipe} 
received his BSc (Hons.) degree in Electronic Engineering from Warwick in 1979 and, after an eight-year period in industry that included running a small company, received his PhD in Robotics from the University of the West of England (UWE) in 1997. Since 2010 he has been a Professor of Robotics and Autonomous Systems at UWE. He was a founding member of the Bristol Robotics Laboratory (BRL), and acted as one of its two Deputy Directors from its inception in 2006 until 2020. His research interests focus on safe and correct operation whilst in close-proximity to human beings. He has co-authored over 200 international refereed publications, supervised 35 PhDs, and created a BRL income of \pounds10M since 2013. He has acted as BRL-UWE PI on the EPSRC grant ‘Trustworthy Robotic Assistants’, the Programme/Hub grants ‘Robotics for Nuclear Environments’ and ‘National Centre for Nuclear Robotics’, and the Centre for Doctoral Training in Robotics and Autonomous Systems. Prof.\ Pipe has been involved with Connected Autonomous Vehicle research and development since 2015 via the Innovate UK/CCAV funded projects VENTURER, FLOURISH, MultiCAV, CAPRI, ROBOPILOT and CAV-Forth.
\end{IEEEbiography}
